Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increases Repair Time?

### 2015-02-23 phaseDelay.tex
Added more references

\documentclass{sig-alternate}
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{wrapfig}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}} 
\newcommand{\lucas}[1]{\textcolor{red}{#1}} 
\newcommand{\bill}[1]{\textcolor{blue}{#1}} 
\newcommand{\carter}[1]{\textcolor{cyan}{#1}} 
%\newenvironment{changed}{\par}{\par}

@@

@@

The TSP couples
the use of integrated product teams with the Personal Software
ProcessSM (PSPSM) to give engineers a defined, planned, and
measured process. For example, PSPSM encourages developers to continually make estimates
about their day-to-day tasks, then compare those estimates against the actual development effort
(in this way, developers can acquire a more realistic understanding of their work behaviour

@@

\fig{sedata} lists some of the publicly available
software projects data sets currently available to 
SE researchers. Most of the \fig{sedata} data sets have software product information
such as full source code, or summaries of static features.
A subset of that data contain issue or defect reports and/or
the time taken to build these systems. Compared to those data
setss, the SEI TSP data contains much more detailed process details
including a detailed phased breakdown showing what happened at what
phases of the lifecycle. The phased used in this paper are shown in \fig{waterfall}. Note that, in that figure:
\bi 
\item
Several  phases have the same  sub-activities of {\em review} and {\em inspect}\footnote{\bill{plz distinguish review and inspect. does one usually happen first?}}
\item Testing is divided into several statges \footnote{\bill{need a one
line description of test vs qualtest vs inttest vs systemTest vs AcceptTest. I tries some words in the Key to \fig{sedata}. dont know if i got it right.}}
\ei

software-related data sets are available to researchers; well
known examples include those from ISBSG (the International
Software Benchmarking Standards Group) and the Promise Data
Repository. The ISBSG provides datasets from more than 5,600
software development projects and publishes data analysis reports
[11]. The Promise Data Repository mainly stores product metrics
of open source software and NASA projects [17]. For a  list
of other Compared to
other data sets, the TSP database provides a granular level of
development detail that enables not only analysis with great
precision at different levels (e.g., project, team, component, and
individual developer), but also additional opportunity to assess
data quality. We hope to make the TSP database more broadly
available in the future to supplement the other research resources

@@

In all data, was collected from 172 separate projects. Given Beck's comments (above) about phase delay motivating agile processes, we take care to identify the differences of these 
projects to agile development projects. In what we call a ``standard agile'' project, there exists
some backlog of tasks. When teams complete their current tasks, they reach into to the backlog
to select the next task(s) to complete. That selection process may use a variety of criteria
to prioritize which  tasks are selected (for more details on that selection process, see~\cite{me09j,port08,boehmturner03}). Tasks are completed in ``sprints'' that can last hours,
days, but rarely not more than weeks. Each day meet for brief ``scrum'' sessions to assess (and possibly alter) their current progress on the goals of the spring.

One way to characterize the above is a ``micro cyclic'' approach where teams 
constantly reassess their priorities using feedback gained after trying to code 
functionality X,Y,Z. An alternate, more traditional approach is a ``macro linear''
approach such as the ``waterfall methodology'' that develops code after an extensive
pre-planning stage:

>>>>

\documentclass{sig-alternate}
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{wrapfig}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}} 
\newcommand{\lucas}[1]{\textcolor{red}{LUCAS: #1}} 
\newcommand{\bill}[1]{\textcolor{blue}{BILL: #1}} 
\newcommand{\carter}[1]{\textcolor{cyan}{CARTER: #1}} 
%\newenvironment{changed}{\par}{\par}

@@

We offer the following notes on the data used in this study.
These notes will be somewhat detailed and we offer them in order
to make the following point:
\bi 
\item The results section of this paper fails to find that  phase delay causing dramatic increases
in time to fix issues;
\item This lack-of-phase-delay effect {\em cannot} be explained away just by  saying that
the projects in this sample adopted something like  agile methods to reduce re-work costs.
\ei

@@

\fig{sedata} lists some of the publicly available
software projects data sets currently available to 
SE researchers. Most of the \fig{sedata} data sets have software product information
such as full source code, or summaries of static features.
A subset of that data contain issue or defect reports and/or
the time taken to build these systems. Compared to those data
setss, the SEI TSP data contains much more detailed process details
including a detailed phased breakdown showing what happened at what
phases of the lifecycle.

As dictacted by the  the projects in our SEI TSP data set  use coaches,
peer review, and  personnel reviews:
a ``coach'' is the team member  authorized to submit project data
(before submission,
these coaches check the data for obvious errors);
``personnel review'' is a technique taken  from the Personal Software
ProcessSM (PSPSM); and
``peer review'' is a standard technique in
traditional software engineering.
PSPSM encourages developers to continually make and review their personnel estimates
about their day-to-day tasks, then compare those estimates against the actual development effort.
In this way, developers can acquire a more realistic understanding of their work behaviour.
As to peer review,  Basili and Boehm write  commented in 2001~\cite{boehm01} 
that peer reviews can catch over half the defects introduced into a system.
Peer review can be conducted on any artifact generated anywhere in the software
lifecycle and can quickly be adapted to new kinds of artifacts.

The phased used in this paper are shown in \fig{waterfall}. Note that, in that figure:
\bi 
\item
Several  phases have the same  sub-activities of {\em review} and {\em inspect}\footnote{\bill{plz distinguish review and inspect. does one usually happen first?}}
\item Testing is divided into several statges \footnote{\bill{need a one
line description of test vs qualtest vs inttest vs systemTest vs AcceptTest. I tries some words in the Key to \fig{sedata}. dont know if i got it right.}}
\ei 
Also shown in \fig{waterfall} (bottom left) is the standard definition of an agile process~\cite{boehmturner03}:
Given some
some backlog of tasks, wgeb teams complete their current tasks, they select the next task(s) to complete. That selection process may use a variety of criteria
to prioritize which  tasks are selected (for more details on that selection process, see~\cite{me09j,port08,boehmturner03}). Tasks are completed in ``sprints'' that can last hours,
days, but rarely not more than weeks. Each day meet for brief ``scrum'' sessions to assess (and possibly alter) their current progress on the goals of the sprint.  
Agile teams race to generate releases
(in the continuous release model, releases can be generated on a daily basis, or even faster).  
Experience gained from those releases informs the discussion in the daily scrums which, in turn,
can inform the team's decisions on how to select and implement the next set of tasks for next sprint.
In fact, that experience can result in changing some/all of the tasks in the current backlog.

TSP is not antithetical to agile--  indeed a TSP-waterfall style project can adopt aspects
of agile.  For example the agile loop  could be applied
over one or more of the phases shown in the long waterfall chain of \fig{waterfall}. Some
TSP teams adopt something like test-driven-development\footnote{TDD is an agile-method
where the ``test'' is the primary driver of the design. The tests are written first,
then the code to support those tests. TDD proceeds in three steps: red (where there
are broken tests); green (where tests are passing); and, possibly, refactor (where
the code is re-organized based on feedback from those tests~\cite{fraser03}.} where
reviews are scheduled after testing. Some of the groups in the SEI TSP data used that approach but
they do not effect the main conclusions of this paper:
\bi 
\item They were strongly in the minority\bill{any numbers on this?};
\item Most of our phase delay data comes from much early in the waterfall model
of \fig{waterfall}.
\ei 
That said, there are some very ``un-agile'' aspects
of the processes used by the   projects in the TSP SEI data.
For teams to be included in this data set they had to be following certain 
 guidelines
laid down by TSPSM (and SEI staff monitored these projects to ensure that that the
following guidelines were maintained\footnote{bill, can you talk at all about your work doing site visits? i.e. how did you ensure compilance with the following}):
\be 
\item  The TSP projects studied here offer new releases at least every three months, but
often much longer that that\bill{any numbers on that}.
\item The TSP projects studied     spend one day (or more) working on 
\item
The time spent in the of a design activity/phase should require 
approximately as much effort as the coding phase. That is, for the projects
studied here, at least half of the reflection on the requirements, design, code
arises without feedback from running code.
\item The teams
cannot combine development and  testing. That is, as before,
it can be days/weeks
before team members in the TSP SEI datatet gain  feedback from executing code.  
\item The time devoted to ``personnel review'' and ``peer review'' (defined below)
is  about 50\% as much effort as the previous construction phase activity.
\ee

@@

The majority of the teams follow a more linear process within a single feature of physical component (usually no more than a week or two work in total). Unlike some agile teams, *most*TSP teams will not conflate development and unit test.

@@

In all data, was collected from 172 separate projects. Given Beck's comments (above) about phase delay motivating agile processes, we take care to identify the differences of these 
projects to agile development projects. An alternate, more traditional approach is a ``macro linear''
approach such as the ``waterfall methodology'' that develops code after an extensive
pre-planning stage:
